Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Building density plots for weibull seed dispersal kernels for each bootstrap

>>>>

```{r}
mycols2 <- c("black", mycols)

weib.curves <- NULL

for(i in 0:5){
  weib.boot %>% 
  filter(indiv == i) -> a

  b <- purrr::map(seq(1:nrow(a)), function(y)
    stat_function(fun = dweibull, args = list(scale = a$est.scale[y], shape = a$est.shape[y]), color = mycols2[i+1], alpha = 0.3))

  weib.curves <- append(weib.curves, b)
}

# ggplot(data = data.frame(x = c(1, 60)), aes(x)) +
#   weib.curves +
#   ylab("Density") + xlab("Distance (m)") +
#   theme_bw()  +
#   theme(legend.position = c(0.7, 0.7),
#         legend.title = element_blank()) 
df %>%
  drop_na(s.id) %>% 
  ggplot(., aes(x = disp)) +
  geom_histogram(aes(y = ..density..), fill = "grey") +
  theme_bw() -> p
# p
# 
# p +
#   stat_function(fun = dweibull, args = list(scale = weib.boot$est.scale[1], shape = weib.boot$est.shape[1]), color = "red")

p + weib.curves
